---
title: "INPUT files"
output:
  BiocStyle::html_document
vignette: |
  %\VignetteIndexEntry{INPUT files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

EPIPE requires two main types of input files:

# IDAT files

A folder containing all the raw IDAT files

# Sample sheet

This file contains metadata and sample information required for processing and analysis. 

Key guidelines for the sample sheet:  

- The sample sheet must be provided in a RDS format (.rds).  

- It must include a ‘Basename’ column that specifies the file paths to the IDAT files. Each entry should provide the full path to the IDAT files for each sample (without the _Grn.idat or _Red.idat extension). For example:  

```{r, eval=FALSE}
inst/extdata/EPICv2/idats/207505140099_R08C01 
```



 

If the Basename column contains the full paths to the IDAT files, the idats_folder parameter in the configuration file can be set to NULL. 

 

- Include a Sample_Name column that contains unique identifiers for each sample. 

- Include a Sentrix_ID column. It must contain the Sentrix ID for each sample. 

- Include a Sentrix_Position column. 

- Also ensure there are no spaces or special characters in the column names of the sample sheet 

 

You can load an example of a sample sheet using the following code:  
```{r, eval=FALSE}
data(samplesheet) 
```
