<!-- # Increment the index -->
`r idx = idx+1` 
<!-- # Generate a dynamic step title -->
## `r paste0("Step ",idx,": Differentially mehtylated CpG regions")`


```{r}
# Display the QC folder path
paths$dmrs_folder
```


As differential methylation CpG positions may not be so informative, differentially methylation regions will be detected using DMRcate R package. 


Thresholds used to filter Differentially methylated CpG positions: 3 minimum CpGs, methylation differences < 0.05 and FDR<0.01 (default).

```{r}

 eval(
   substitute(
     dmrs_f <- tar_read(dmrs_f_n),
     env = list(dmrs_f_n=paste0("dmrs_f_",values_row$data_names))
     )
   )
if (nrow(dmrs_f)>0){
  message<-' - Summary of differentially methylated regions per each contrast:' 
}else{
  message<-' - No differential mehtylation regions were found'
}
```


`r message`


```{r}

# if (nrow(dmrs_f)>0){
#   #dmrs_f<-tar_read(dmrs_f_ex_EPICv2)
#   # Create a table with a summary of DMPs per each type
# 
#   count_dmrs<-as.data.frame(table(dmrs_f$Contrast))
#   count_dmrs$Var1<-as.character(count_dmrs$Var1)
#   total_row<-list(Var1 = "Total", Freq = length(dmrs_f$Contrast))
#   count_dmrs <- rbind(count_dmrs, total_row)
# 
#   colnames(count_dmrs)<-c('Contrasts','Num.DMR')
# 
# 
#   knitr::kable(count_dmrs,format = "html")
# }

if (nrow(dmrs_f)>0){
  eval(
     substitute(
       dmrs_summary <- tar_read(dmrs_summary_n),
       env = list(dmrs_summary_n=paste0("dmrs_summary_",values_row$data_names))
       )
     )
  
   knitr::kable(dmrs_summary,format = "html")
}

```



### DMR genes and enrichment 

The aim of this step is to identify which biological pathways are over represented in those differentially methylated CpGs. Gprofiiler2 R package is used to perform functional enrichment analysis.



```{r}
if (nrow(dmrs_f)>0){
  message<-''
}else{
  message<-'No genes and therefore, no pathways are found'
}
```

`r message`



```{r}
if (nrow(dmrs_f)>0){
  message<-'#### Enrichment plot of all the pathways per each contrast: '
 
}else{
  message<-NULL
 
}
```

`r message`



```{r}
# DMP plots
# number depending on contrasts
#dmrs_f<-tar_read(dmrs_f_ex_EPICv2)
markdown_text <- NULL
if (nrow(dmrs_f)>0){
  custom_paths<-tar_read(custom_paths_ex_EPICv2)
  # Get the list of contrast names
  contrast_names <- unique(dmrs_f$Contrast)
  
  
  # Loop over each contrast
  for (contrast in contrast_names) {
    # Generate the image file path
    image_path <- file.path(paths$pathway_folder, paste0("DMRs/table_plot_", contrast, ".png"))
    
    # Display the image
    markdown_text <- c(markdown_text, paste0("![", contrast, "](", image_path, ")"))
    #cat("![",contrast,"](`r ",image_path,"`)\n\n")
    
    
  }
}else{
  markdown_text <- NULL
}


```


`r markdown_text`




```{r}
if (nrow(dmrs_f)>0){
  message<-'You can also visualize the plot interactively, which it is found within gopath/DMRs folder'
}else{
  message<-NULL
}
```


`r message`




### Summary

It can be useful to visualize a general summary of all the differential methylation positions and regions found per each contrast. This summary is stored in the following directory: 

```{r}
# Display the QC folder path
paste0(paths$results_folder,values_row$data_names)
```



```{r,message=FALSE}
#path<-paths$results_folder
#custom_paths<-tar_read(custom_paths_ex_EPICv2)
#path<-custom_paths$results_folder


eval(
   substitute(
     summary_f <- tar_read(summaries_n),
     env = list(summaries_n=paste0("sumaries_",values_row$data_names))
     )
   )

 knitr::kable(summary_f,format = "html")





```




